## `r s`.2 Global analysis
### `r s`.2.1 Global resampling
```{r}
inclusions=globalInclusions
```

```{r child = 'permutationTest.Rmd'}
```
### `r s`.2.2 Local resampling
constraint resampling to preserve the same amount of predictions accross each set
```{r}
resamplingGroups=cbind(Lset0,Lset1,Lset2,Lset3)
```

```{r child = 'permutationTestStrat.Rmd'}
```

```{r}
table=cbind("global",results)
```
## `r s`.3 Permutation test for the set0
set 0 = one operation only
(formulas like (T1-d), (P1-d), etc....)
```{r}
inclusions=Lset0 & globalInclusions
```

```{r child = 'permutationTest.Rmd'}
```
```{r}
results=cbind("set0",results)
table=rbind(table,results)
```
## `r s`.4  permutation test for the set1
set 0 = one operation only
(formulas like (T1-d)+P1, (P1+T1)-d, etc....)
```{r}
inclusions=Lset1 & globalInclusions
```

```{r child = 'permutationTest.Rmd'}
```
```{r}
results=cbind("set1",results)
table=rbind(table,results)
```
## `r s`.5 permutation test for the set2
set 2 = two operation only, one operand used twice
(formulas like (T1-d)+T1, (P1+T1)+P1, etc....)
```{r}
inclusions=Lset2 & globalInclusions
```

```{r child = 'permutationTest.Rmd'}
```
```{r}
results=cbind("set2",results)
table=rbind(table,results)
```
## `r s`.6 permutation test for the set3
set 2 = two operation only, one operand used twice
(formulas like (T1-d)+(P1-d), (P1+T1)+(P1+d), etc....)
```{r}
inclusions=Lset3 & globalInclusions
```
```{r child = 'permutationTest.Rmd'}
```

```{r}
results=cbind("set3",results)
table=rbind(table,results)
table
```

```{r echo=FALSE, results='hide'}
s=s+1
```
