```{r}
datasTemp<-datas[inclusions,]
predictionsTemp<-currentPredictions[inclusions]

numberOfFormulas=nrow(datasTemp)
numberOfSelectedFormulas=sum(predictionsTemp)
numberOfOccurencesInSelectedFormulas=sum(datasTemp$occurrences[predictionsTemp])
numberOfOccurences=sum(datasTemp$occurrences)
results=NULL
```

A random model is better than our model if it captures    
(1) more than numberOfOccurencesInSelectedFormulas=`r numberOfOccurencesInSelectedFormulas` amongst a total of numberOfOccurences=`r numberOfOccurences`    
(2) by selecting numberOfSelectedFormulas=`r numberOfSelectedFormulas` formula 
amongst numberOfFormulas=`r numberOfFormulas` possible formulas.

Summary notation : `r numberOfSelectedFormulas` over `r numberOfFormulas` predictions which captures `r numberOfOccurencesInSelectedFormulas` over a total of `r numberOfOccurences` occurences
**Computation of RelativeStrengh**
```{r}
Pv= numberOfOccurencesInSelectedFormulas/numberOfOccurences
k=numberOfSelectedFormulas/numberOfFormulas
RelativeStrengh=round((numberOfOccurencesInSelectedFormulas/numberOfSelectedFormulas)/((numberOfOccurences-numberOfOccurencesInSelectedFormulas)/(numberOfFormulas-numberOfSelectedFormulas)),2)
```
RelativeStrengh : predicted formulas get `r RelativeStrengh` times more occurences than non predicted formulas
**Bootstraping confidence intervall of RelativeStrengh**
```{r}
FullDataTemp=cbind(predictionsTemp,datasTemp)
boot=c()
CI=c()
for ( i in 1:maxResampling) {
  cases=sample(numberOfFormulas,numberOfFormulas,replace=TRUE)#replace = TRUE for bootstraping
  datasTemp2=FullDataTemp[cases,]
  randomPredictions=datasTemp2$predictionsTemp
  numberOfSelectedFormulas_rd=sum(randomPredictions)
  numberOfOccurencesInSelectedFormulas_rd=sum(datasTemp2$occurrences[randomPredictions])
  numberOfOccurences_rd=sum(datasTemp2$occurrences)
  RelativeStrengh_i=round((numberOfOccurencesInSelectedFormulas_rd/numberOfSelectedFormulas_rd)/((numberOfOccurences_rd-numberOfOccurencesInSelectedFormulas_rd)/(numberOfFormulas-numberOfSelectedFormulas_rd)),2)
  boot[i]<-RelativeStrengh_i
}
CI=round(quantile(boot,probs=c(0.025,0.975),na.rm=TRUE),2)
```

```{r}

count=0
for ( i in 1:maxResampling) {
  randomSelection=sample(predictionsTemp,replace=FALSE)
  captures=sum(datasTemp$occurrences[randomSelection])
  if (captures>=numberOfOccurencesInSelectedFormulas) {
  count=count+1
  }
}
pvalue=count/maxResampling
```
La p-value obtenue par permutation est égale à pvalue=`r pvalue`    
```{r results='hide',echo=FALSE}
proba=numberOfSelectedFormulas/numberOfFormulas
if(numberOfOccurences!=0){
b=binom.test(numberOfOccurencesInSelectedFormulas,numberOfOccurences, p = proba,alternative = "greater",conf.level = 0.95)
}else{
print("can't be computed")
}
```
A titre indicatif un test binomial aurait donné une p-value de `r b$p.value` (Bloc de code non affiché pour ne pas surcharger)


```{r}
RatioPredictions=paste0(numberOfSelectedFormulas,"/",numberOfFormulas) 
RatioCaptures=paste0(numberOfOccurencesInSelectedFormulas,"/",numberOfOccurences) 
results=cbind(RatioPredictions,RatioCaptures,pvalue,paste0(RelativeStrengh,"(",CI[1],"-",CI[2],")"))
```
