```{r}
datasTemp<-datas[inclusions,]
predictionsTemp<-currentPredictions[inclusions]

numberOfFormulas=nrow(datasTemp)
numberOfSelectedFormulas=sum(predictionsTemp)
numberOfOccurencesInSelectedFormulas=sum(datasTemp$occurrences[predictionsTemp])
numberOfOccurences=sum(datasTemp$occurrences)
results=NULL
```

A random model is better than our model if it captures    
(1) more than numberOfOccurencesInSelectedFormulas=`r numberOfOccurencesInSelectedFormulas` amongst a total of numberOfOccurences=`r numberOfOccurences`    
(2) by selecting numberOfSelectedFormulas=`r numberOfSelectedFormulas` formula 
amongst numberOfFormulas=`r numberOfFormulas` possible formulas.

Summary notation : `r numberOfSelectedFormulas` over `r numberOfFormulas` predictions which captures `r numberOfOccurencesInSelectedFormulas` over a total of `r numberOfOccurences` occurences
```{r results='hide',echo=FALSE}
Pv= numberOfOccurencesInSelectedFormulas/numberOfOccurences
k=numberOfSelectedFormulas/numberOfFormulas
Pcor=round((Pv-k)/(1-k),3)
```
Pcor : `r Pcor*100` % 

```{r}

count=0
for ( i in 1:maxBootstrap) {
  randomSelection=sample(predictionsTemp)
  captures=sum(datasTemp$occurrences[randomSelection])
  if (captures>=numberOfOccurencesInSelectedFormulas) {
  count=count+1
  }
}
pvalue=count/maxBootstrap
```
La p-value obtenue par permutation est égale à pvalue=`r pvalue`    
```{r results='hide',echo=FALSE}
proba=numberOfSelectedFormulas/numberOfFormulas
b=binom.test(numberOfOccurencesInSelectedFormulas,numberOfOccurences, p = proba,alternative = "greater",conf.level = 0.95)
```
A titre indicatif un test binomial aurait donné une p-value de `r b$p.value` (Bloc de code non affiché pour ne pas surcharger)


```{r}
RatioPredictions=paste(numberOfSelectedFormulas,"/",numberOfFormulas) 
RatioCaptures=paste(numberOfOccurencesInSelectedFormulas,"/",numberOfOccurences) 
results=cbind(RatioPredictions,RatioCaptures,pvalue,Pcor)
```
